{\bf {\Large Four decades of water quality change in the upper San Francisco Estuary}}

### 2017-10-09 sftrends_manu.Rnw
fixed table formats - one star for sig, no bold-italic

# percent changes
tab <- trnds_nrm %>% 
  filter(cat %in% c('1976-1995', '1996-2013')) %>% 
  select(Site_Code, resvar, cat, med, perchg, ztest) %>% 
  mutate(
    med = round(med, 1), 
    perchg = round(perchg, 1),
    perchg = ifelse(
      perchg < 0, 
      paste0('(', perchg, ')' ), 
      paste0('(\\textit{\\textbf{', perchg, '}})')
      ), 
    ztest = p_ast(ztest)
  ) %>% 
  unite('perchg', perchg, ztest, sep = '') %>% 
  mutate(
    perchg = paste0('\\footnotesize{', perchg, '}')
  ) %>% 
  unite('val', med, perchg, sep = ' ') %>% 
  spread(cat, val) %>% 
  arrange(resvar, Site_Code) %>% 
  select(Site_Code, resvar, `1976-1995`, `1996-2013`)

# table stuff
cap.val <- 'Summaries of flow-normalized trends in nitrogen analytes for all stations and annual aggregations'
foot.val<-'\\footnotesize Summaries are  medians (mg L$^{-1}$) and percent change per year in parentheses (increasing in bold-italic). Changes and significance estimates are based on seasonal Kendall tests of flow-normalized results within each time period. *$p<0.05$; **$p<0.005$'
vars <- c('DIN', 'NH$_{4}^{+}$', 'NO$_{2}^{-}$/NO$_{3}^{2-}$')
stats <- tab$Site_Code

@@

# percent changes
tab <- trnds_nrm %>% 
  filter(
    cat %in% c('Spring', 'Summer', 'Fall', 'Winter') &
    ann %in% 'bef'
    ) %>% 
  select(Site_Code, resvar, cat, med, perchg, ztest) %>% 
  mutate(
    med = round(med, 1), 
    perchg = round(perchg, 1),
    perchg = ifelse(
      perchg < 0, 
      paste0('(', perchg, ')' ), 
      paste0('(\\textit{\\textbf{', perchg, '}})')
      ), 
    ztest = p_ast(ztest)
  ) %>% 
  unite('perchg', perchg, ztest, sep = '') %>% 
  mutate(
    perchg = paste0('\\footnotesize{', perchg, '}')
  ) %>% 
  unite('val', med, perchg, sep = ' ') %>% 
  spread(cat, val) %>% 
  arrange(resvar, Site_Code)

# table stuff
cap.val <- 'Summaries of flow-normalized trends in nitrogen analytes for all stations and seasonal aggregations from 1976-1995'
foot.val<-'\\footnotesize Summaries are  medians (mg L$^{-1}$) and percent change per year in parentheses (increasing in bold-italic). Changes and significance estimates are based on seasonal Kendall tests of flow-normalized results within each time period. Months for each season are Spring: MAM, Summer: JJA, Fall: SON, Winter: DJF. *$p<0.05$; **$p<0.005$'
vars <- c('DIN', 'NH$_{4}^{+}$', 'NO$_{2}^{-}$/NO$_{3}^{2-}$')
stats <- tab$Site_Code

@@

# percent changes
tab <- trnds_nrm %>% 
  filter(
    cat %in% c('Spring', 'Summer', 'Fall', 'Winter') &
    ann %in% 'aft'
    ) %>% 
  select(Site_Code, resvar, cat, med, perchg, ztest) %>% 
  mutate(
    med = round(med, 1), 
    perchg = round(perchg, 1),
    perchg = ifelse(
      perchg < 0, 
      paste0('(', perchg, ')' ), 
      paste0('(\\textit{\\textbf{', perchg, '}})')
      ), 
    ztest = p_ast(ztest)
  ) %>% 
  unite('perchg', perchg, ztest, sep = '') %>% 
  mutate(
    perchg = paste0('\\footnotesize{', perchg, '}')
  ) %>% 
  unite('val', med, perchg, sep = ' ') %>% 
  spread(cat, val) %>% 
  arrange(resvar, Site_Code)

# table stuff
cap.val <- 'Summaries of flow-normalized trends in nitrogen analytes for all stations and seasonal aggregations from 1996-2013'
foot.val<-'\\footnotesize Summaries are  medians (mg L$^{-1}$) and percent change per year in parentheses (increasing in bold-italic). Changes and significance estimates are based on seasonal Kendall tests of flow-normalized results within each time period. Months for each season are Spring: MAM, Summer: JJA, Fall: SON, Winter: DJF. *$p<0.05$; **$p<0.005$'
vars <- c('DIN', 'NH$_{4}^{+}$', 'NO$_{2}^{-}$/NO$_{3}^{2-}$')
stats <- tab$Site_Code

@@

# combine for trends for table
totab <- rbind(no_bf, no_af, nh_bf, nh_af) %>% 
  select(-tau, -slope, -chitest) %>% 
  mutate(
    med = round(med, 1), 
    perchg = round(perchg, 1),
    perchg = ifelse(
      perchg < 0, 
      perchg, 
      paste0('\\textit{\\textbf{', perchg, '}}')
      ), 
    ztest = p_ast(ztest)
  ) %>% 
  unite('perchg', perchg, ztest, sep = '') %>% 
  gather('est', 'val', med:perchg) %>% 
  unite('col', var, est) %>% 
  spread(col, val) %>% 
  unite('period', cat, period) %>% 
  mutate(period = factor(period, levels = faclevs, labels = faclevs)) %>% 
  arrange(period) %>% 
  mutate(cat = c(yrlabs_bf, yrlabs_af, molabs, molabs)) %>% 
  data.frame(sep = c(rep('Annual', 2), rep('Seasonal, pre', 4), rep('Seasonal, post', 4)), .) %>% 
  select(sep, cat, no_med, no_perchg, nh_med, nh_perchg)

@@

cap.val<-'Summaries of flow-normalized trends in nitrite/nitrate and ammonium (mg L$^{-1}$) concentrations before and after \\ac{wwtp} upgrades upstream of station P8'
foot.val<-'\\footnotesize Upgrades were completed in 2006 at the City of Stockton \\ac{wwtp} (San Joaquin County, \\cref{fig:stock}). Summaries are  medians and percent change per year in parentheses (increasing in bold-italic).  Changes and significance estimates are based on seasonal Kendall tests of flow-normalized results within each time period. Increasing values are in bold-italics. Months for each season are Spring: MAM, Summer: JJA, Fall: SON, Winter: DJF. *$p<0.05$; **$p<0.005$'

>>>>

# percent changes
tab <- trnds_nrm %>% 
  filter(cat %in% c('1976-1995', '1996-2013')) %>% 
  select(Site_Code, resvar, cat, med, perchg, ztest) %>% 
  mutate(
    med = round(med, 1), 
    perchg = round(perchg, 1),
    perchg = ifelse(
      perchg < 0, 
      paste0('(', perchg, ')' ), 
      paste0('(\\textbf{', perchg, '})')
      ), 
    ztest = p_ast(ztest)
  ) %>% 
  unite('perchg', perchg, ztest, sep = '') %>% 
  mutate(
    perchg = paste0('\\footnotesize{', perchg, '}')
  ) %>% 
  unite('val', med, perchg, sep = ' ') %>% 
  spread(cat, val) %>% 
  arrange(resvar, Site_Code) %>% 
  select(Site_Code, resvar, `1976-1995`, `1996-2013`)

# table stuff
cap.val <- 'Summaries of flow-normalized trends in nitrogen analytes for all stations and annual aggregations'
foot.val<-'\\footnotesize Summaries are  medians (mg L$^{-1}$) and percent change per year in parentheses (increasing in bold). Changes and significance estimates are based on seasonal Kendall tests of flow-normalized results within each time period. *$p<0.05$'
vars <- c('DIN', 'NH$_{4}^{+}$', 'NO$_{2}^{-}$/NO$_{3}^{2-}$')
stats <- tab$Site_Code

@@

# percent changes
tab <- trnds_nrm %>% 
  filter(
    cat %in% c('Spring', 'Summer', 'Fall', 'Winter') &
    ann %in% 'bef'
    ) %>% 
  select(Site_Code, resvar, cat, med, perchg, ztest) %>% 
  mutate(
    med = round(med, 1), 
    perchg = round(perchg, 1),
    perchg = ifelse(
      perchg < 0, 
      paste0('(', perchg, ')' ), 
      paste0('(\\textbf{', perchg, '})')
      ), 
    ztest = p_ast(ztest)
  ) %>% 
  unite('perchg', perchg, ztest, sep = '') %>% 
  mutate(
    perchg = paste0('\\footnotesize{', perchg, '}')
  ) %>% 
  unite('val', med, perchg, sep = ' ') %>% 
  spread(cat, val) %>% 
  arrange(resvar, Site_Code)

# table stuff
cap.val <- 'Summaries of flow-normalized trends in nitrogen analytes for all stations and seasonal aggregations from 1976-1995'
foot.val<-'\\footnotesize Summaries are  medians (mg L$^{-1}$) and percent change per year in parentheses (increasing in bold). Changes and significance estimates are based on seasonal Kendall tests of flow-normalized results within each time period. Months for each season are Spring: MAM, Summer: JJA, Fall: SON, Winter: DJF. *$p<0.05$'
vars <- c('DIN', 'NH$_{4}^{+}$', 'NO$_{2}^{-}$/NO$_{3}^{2-}$')
stats <- tab$Site_Code

@@

# percent changes
tab <- trnds_nrm %>% 
  filter(
    cat %in% c('Spring', 'Summer', 'Fall', 'Winter') &
    ann %in% 'aft'
    ) %>% 
  select(Site_Code, resvar, cat, med, perchg, ztest) %>% 
  mutate(
    med = round(med, 1), 
    perchg = round(perchg, 1),
    perchg = ifelse(
      perchg < 0, 
      paste0('(', perchg, ')' ), 
      paste0('(\\textbf{', perchg, '})')
      ), 
    ztest = p_ast(ztest)
  ) %>% 
  unite('perchg', perchg, ztest, sep = '') %>% 
  mutate(
    perchg = paste0('\\footnotesize{', perchg, '}')
  ) %>% 
  unite('val', med, perchg, sep = ' ') %>% 
  spread(cat, val) %>% 
  arrange(resvar, Site_Code)

# table stuff
cap.val <- 'Summaries of flow-normalized trends in nitrogen analytes for all stations and seasonal aggregations from 1996-2013'
foot.val<-'\\footnotesize Summaries are  medians (mg L$^{-1}$) and percent change per year in parentheses (increasing in bold). Changes and significance estimates are based on seasonal Kendall tests of flow-normalized results within each time period. Months for each season are Spring: MAM, Summer: JJA, Fall: SON, Winter: DJF. *$p<0.05$'
vars <- c('DIN', 'NH$_{4}^{+}$', 'NO$_{2}^{-}$/NO$_{3}^{2-}$')
stats <- tab$Site_Code

@@

# combine for trends for table
totab <- rbind(no_bf, no_af, nh_bf, nh_af) %>% 
  select(-tau, -slope, -chitest) %>% 
  mutate(
    med = round(med, 1), 
    perchg = round(perchg, 1),
    perchg = ifelse(
      perchg < 0, 
      perchg, 
      paste0('\\textbf{', perchg, '}')
      ), 
    ztest = p_ast(ztest)
  ) %>% 
  unite('perchg', perchg, ztest, sep = '') %>% 
  gather('est', 'val', med:perchg) %>% 
  unite('col', var, est) %>% 
  spread(col, val) %>% 
  unite('period', cat, period) %>% 
  mutate(period = factor(period, levels = faclevs, labels = faclevs)) %>% 
  arrange(period) %>% 
  mutate(cat = c(yrlabs_bf, yrlabs_af, molabs, molabs)) %>% 
  data.frame(sep = c(rep('Annual', 2), rep('Seasonal, pre', 4), rep('Seasonal, post', 4)), .) %>% 
  select(sep, cat, no_med, no_perchg, nh_med, nh_perchg)

@@

cap.val<-'Summaries of flow-normalized trends in nitrite/nitrate and ammonium (mg L$^{-1}$) concentrations before and after \\ac{wwtp} upgrades upstream of station P8'
foot.val<-'\\footnotesize Upgrades were completed in 2006 at the City of Stockton \\ac{wwtp} (San Joaquin County, \\cref{fig:stock}). Summaries are  medians and percent change per year in parentheses (increasing in bold).  Changes and significance estimates are based on seasonal Kendall tests of flow-normalized results within each time period. Increasing values are in bold-italics. Months for each season are Spring: MAM, Summer: JJA, Fall: SON, Winter: DJF. *$p<0.05$'
